\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-06-13 Manuscript/manuscript.tex
Added explanation of venue/heat effect

\subsection{GLMM}\label{sec:glmm}
Based on an exploratory analysis using the GLMM model for the reaction times
from the World Championships, we chose a gamma mixed-effect model as our 
final model. As suggested by the log-likelihood and the Akaike Information
Criterion (AIC), the normal error model on the log-scale was found to be
much inferior to the gamma model which better captures the skewness of the
data. Two random effects were found useful: one capturing the venue effect in
each year and the other capturing the heat effect within each year. The heat
effect is important as it captures the variability in the amount of time
athletes are on the starting blocks before the gun goes off. Thus, we can try
to reduce this variability by accounting for it in the model through the heat
effect.

>>>>

\subsection{GLMM}\label{sec:glmm}
Based on an exploratory analysis using the GLMM model for the reaction times
from the World Championships, we chose a gamma mixed-effect model as our 
final model. As suggested by the log-likelihood and the Akaike Information
Criterion (AIC), the normal error model on the log-scale was found to be
much inferior to the gamma model which better captures the skewness of the
data. Two random effects were found useful: one capturing the venue effect, which
is used to contrast years, and the second being the heat effect, where every
race was given a unique identifier with typically five to nine observations
per race. The heat effect is important as it captures the variability in the
amount of time athletes are on the starting blocks before the gun goes off.
Thus, we can try to reduce this variability by accounting for it in the model
through the heat effect.
